Multi sky-view\\ 3D aerosol distribution recovery

### 2013-10-08 article.tex
Updated absorbtion error

\noindent{\bf Forward models and distributions}:
\Cref{fig:results} shows estimation results, corresponding to the
original distributions of \cref{fig:distributions}.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/results}}
  \caption{\small Recoveries of scenes shown in
    \cref{fig:distributions}. Color represents aerosol density, in
    units of $10^{6}~{\rm particles}/{\rm m}^3.$ In (a) and (b)
    images simulated by single-scattering are used as input for the
    recovery.  In (c) and (d), MC simulated images are used as input for the
    recovery.  }
  \label{fig:results}
\end{figure}
Here, the atmosphere domain was defined over a
$20\times20 \times 40$ grid. Cameras were placed
$\sim 7$km apart on a $6\times6$ grid.
In Figs.~\ref{fig:results}(a) and \ref{fig:results}(b), the single-scattering model was
used both in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}(c) and \ref{fig:results}(d), the MC model (multiple scattering)
rendered the raw images, over which our recovery (Sec.~\ref{sec:inverse-problem}) was tested.
Overall, the distributions, the density order of magnitude and values are consistent.
Errors in Figs.~\ref{fig:results}(a) and \ref{fig:results}(b) stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in
\newcolumntype{g}{>{\columncolor{Gray}}r}
\begin{table}[t]
  \centering
  \begin{tabular}{cccccgg}
    \toprule
    Haze   & Forward        & Aerosol                 & Isotropic       & Absorbing & $\delta_{\rm mass}$ & $\epsilon~~$ \\
    scene  & model          & density [$1/{\rm m}^3$] & phase function? & aerosol?  &                     &              \\
     \midrule                                                                                             
    Front  & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & -1.1\%               & 18\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & 14\%               & 65\%         \\
    \cmidrule(r){1-5}                                                                                     
     Blobs & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & 0\%                 & 14\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & -6.7\%               & 65\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ & $\surd$         &           & 2\%                & 49\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 & $\surd$   & -9.6\%               & 83\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{7})$ &                 &           & -23\%                & 98\%         \\
    \bottomrule
  \end{tabular}
  \caption{Relative errors in various simulations. Here ${\mathcal{O}}$ denotes order of magnitude.}
  \label{tbl:mass}
\end{table}
the algorithm of \cref{sec:inverse-problem}. \\

>>>>

\noindent{\bf Forward models and distributions}:
\Cref{fig:results} shows estimation results, corresponding to the
original distributions of \cref{fig:distributions}.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/results}}
  \caption{\small Recoveries of scenes shown in
    \cref{fig:distributions}. Color represents aerosol density, in
    units of $10^{6}~{\rm particles}/{\rm m}^3.$ In (a) and (b)
    images simulated by single-scattering are used as input for the
    recovery.  In (c) and (d), MC simulated images are used as input for the
    recovery.  }
  \label{fig:results}
\end{figure}
Here, the atmosphere domain was defined over a
$20\times20 \times 40$ grid. Cameras were placed
$\sim 7$km apart on a $6\times6$ grid.
In Figs.~\ref{fig:results}(a) and \ref{fig:results}(b), the single-scattering model was
used both in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}(c) and \ref{fig:results}(d), the MC model (multiple scattering)
rendered the raw images, over which our recovery (Sec.~\ref{sec:inverse-problem}) was tested.
Overall, the distributions, the density order of magnitude and values are consistent.
Errors in Figs.~\ref{fig:results}(a) and \ref{fig:results}(b) stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in
\newcolumntype{g}{>{\columncolor{Gray}}r}
\begin{table}[t]
  \centering
  \begin{tabular}{cccccgg}
    \toprule
    Haze   & Forward        & Aerosol                 & Isotropic       & Absorbing & $\delta_{\rm mass}$ & $\epsilon~~$ \\
    scene  & model          & density [$1/{\rm m}^3$] & phase function? & aerosol?  &                     &              \\
     \midrule                                                                                             
    Front  & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & -1.1\%               & 18\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & 14\%               & 65\%         \\
    \cmidrule(r){1-5}                                                                                     
     Blobs & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & 0\%                 & 14\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & -6.7\%               & 65\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ & $\surd$         &           & 2\%                & 49\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 & $\surd$   & -5.7\%               & 80\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{7})$ &                 &           & -23\%                & 98\%         \\
    \bottomrule
  \end{tabular}
  \caption{Relative errors in various simulations. Here ${\mathcal{O}}$ denotes order of magnitude.}
  \label{tbl:mass}
\end{table}
the algorithm of \cref{sec:inverse-problem}. \\
